Graph Storage: How good is CSR really?

### 2017-12-09 Seminar Paper/paper.tex
std::list picture is updated
std::vector and CSR pic are updated

\begin{tikzpicture}[>=latex]
\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (1,1) 
(mat1)
{
0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & \\
1 & 2 & 3 & 4 & 1 & 4 & 2 & 3 & \\
};
\matrix[mymat,below=of mat1,row 2/.style={nodes=draw}]
at (4,0.7)
(mat2)
{
  &   &   &  &  \\
0 & 3 & 4 & 6 & 8\\
};

@@

    \node[head, label=below:head of 1] (head1) {};
    \node[data, right of=head1]    (A1) {1};
    \node[data, right of=A1]       (B1) {2};
    \node[data, right of=B1]       (C1) {3 \nodepart{second} null};

@@

\begin{tikzpicture}[>=latex]
\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (1,1) 
(mat1)
{
 &  &  & \\
1 & 2 & 3 & \phantom{x}\\
};
\node[] at (0.15,0.93)
  (cella) {\texttt{edges[1]}};

>>>>

\begin{tikzpicture}[>=latex]
\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (1,1) 
(mat1)
{
0 & 1 & 2 & 3 & 4 & 5 & 6 & 7 & \\
2 & 3 & 4 & 4 & 1 & 4 & 2 & 3 & \\
};
\matrix[mymat,below=of mat1,row 2/.style={nodes=draw}]
at (4,0.7)
(mat2)
{
  &   &   &  &  \\
0 & 3 & 4 & 6 & 8\\
};

@@

    \node[head, label=below:head of 1] (head1) {};
    \node[data, right of=head1]    (A1) {2};
    \node[data, right of=A1]       (B1) {3};
    \node[data, right of=B1]       (C1) {4 \nodepart{second} null};

@@

\begin{tikzpicture}[>=latex]
\matrix[mymat,anchor=west,row 2/.style={nodes=draw}]
at (1,1) 
(mat1)
{
 &  &  & \\
2 & 3 & 4 & \phantom{x}\\
};
\node[] at (0.15,0.93)
  (cella) {\texttt{edges[1]}};
